\documentclass[10pt]{article}
\usepackage[letterpaper,landscape,margin=0.42in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{multicol}
\usepackage{microtype}
\usepackage{graphicx}
\input{../paper/release_info}
\pagestyle{empty}

\definecolor{ophblue}{RGB}{10,52,85}
\definecolor{ophlight}{RGB}{239,246,252}
\definecolor{ophgold}{RGB}{255,245,210}
\definecolor{ophgreen}{RGB}{230,248,236}
\definecolor{ophline}{RGB}{150,176,200}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0.22em}
\setlength{\abovedisplayskip}{0.32em}
\setlength{\belowdisplayskip}{0.32em}
\setlength{\columnsep}{0.28in}
\tcbset{enhanced,arc=1.2mm,boxrule=0.5pt,left=1.2mm,right=1.2mm,top=0.75mm,bottom=0.75mm,before skip=0.32em,after skip=0.32em,colframe=ophline}
\newtcolorbox{banner}{colback=ophlight,colframe=ophline}
\newtcolorbox{resultbox}{colback=ophgold,colframe=ophblue}
\newtcolorbox{greenbox}{colback=ophgreen,colframe=ophblue}
\newcommand{\sect}[1]{\vspace{0.24em}{\bfseries\color{ophblue}#1}\par}

\begin{document}
\fontsize{8.3pt}{9.35pt}\selectfont

{\LARGE\bfseries\color{ophblue}Compact OPH gravity proof}\hfill
{\normalsize Newton's constant as the area-law readout}\par
{\scriptsize Paper release: \texttt{\OPHPaperReleaseID}\quad Released: \OPHPaperReleaseDate}\par
\begin{banner}
\centering
{\Large\bfseries observation locates the basin; OPH fixed-point uniqueness removes freedom.}
\end{banner}

\begin{multicols}{3}
\raggedcolumns

\sect{1. Starting hypothesis}
OPH starts with this hypothesis: reality is a closed mathematical simulation
that contains itself, its observers, and its own readout rules.  The clock is
inside the structure: observers experience an ordered stream of records, and
that ordered stream is subjective time.

The constants of nature are coordinates of the closed structure.  A coordinate
can exist before any observer computes it.  Measurement tells an observer which
basin of the mathematical map is being experienced.

\begin{greenbox}
\textbf{Operational rule.}
We guess a value from the observed universe, place that guess inside the
corresponding OPH basin, and calculate the fixed point.  The guess locates a
branch.  The fixed point removes the numerical freedom.
\end{greenbox}

\sect{2. The fixed-point move}
Let \(X\) be a complete metric space and let \(I\subset X\) be the observed
branch interval.  Let \(F:I\to I\) be the OPH readback law for that branch.
The certificate is
\[
  F(I)\subseteq I,\qquad
  d(F(x),F(y))\le q\,d(x,y),\qquad 0\le q<1 .
\]
Banach's theorem gives exactly one fixed point
\[
  x_\star=F(x_\star).
\]
For every initial guess \(x_0\in I\),
\[
  x_{n+1}=F(x_n)
  \quad\Longrightarrow\quad
  x_n\to x_\star .
\]
The observed universe supplies \(x_0\).  The closure law supplies \(x_\star\).
Approximate observation locates the branch.  The contraction certificate gives
the exact value.

\columnbreak

\sect{3. The two OPH variables}
The compact OPH closure architecture has two named closure coordinates.

\[
  \boxed{P}\qquad\hbox{local observer-cell pixel ratio}
\]
\[
  \boxed{N}\qquad\hbox{global closed-screen capacity}
\]

\(P\) is local.  It states how much screen area one elementary observer cell
carries and how much shared edge entropy the same cell contributes.

\(N\) is global.  It counts the capacity of the closed screen and fixes the
dimensionless de Sitter capacity branch.

On the selected branches, \(P_\star\) and \(N_\star\) are the unique fixed
points of their OPH readback laws.  Gravity also uses the separate SI scale
certificate stated on the next page.

\sect{4. Local closure for \(P\)}
The local pixel is fixed by the outer/inner observer-cell closure
\[
  P=\Gamma(P)=\varphi+\frac{\sqrt\pi}{A_T(P)} .
\]
On the physical interval \(I_P\),
\[
  \Gamma(I_P)\subseteq I_P,\qquad
  |\Gamma'(P)|\le q_P<1 .
\]
Therefore
\[
  P_\star=\Gamma(P_\star)
\]
is unique.  For gravity, \(P_\star\) defines the local cell area and the local
edge entropy.  It cancels from the final readout.

\sect{5. Global closure for \(N\)}
The global screen branch is the fixed point of the closed capacity readback
\[
  N=\mathcal C(N).
\]
With logarithmic metric on the physical interval \(I_N\),
\[
  \mathcal C(I_N)\subseteq I_N,\qquad
  d(\mathcal C(N_1),\mathcal C(N_2))\le q_Nd(N_1,N_2),
  \qquad q_N<1 .
\]
Hence
\[
  N_\star=\mathcal C(N_\star)
\]
is unique.
The capacity coordinate has count form
\[
  N_\star=\operatorname{MAR}\arg\max_N\Psi(N),
  \qquad
  \Psi(N)=\log|\Omega_N^{\rm sc}|-N .
\]
Strict concavity of \(\Psi\), with one zero of \(\Psi'\), gives one capacity
maximizer.  A rough branch display is
\[
  N_\star\simeq3.31\times10^{122}.
\]
This is the de Sitter entropy-capacity scale, not the high-precision input for
the gravity row.  If \(R_{\rm dS}\) is the late-time static-patch radius, then
\[
  N_{\rm scr}=S_{\rm dS}
  =
  \frac{A_{\rm dS}}{4\ell_\star^2}
  =
  \pi\left(\frac{R_{\rm dS}}{\ell_\star}\right)^2 .
\]

\end{multicols}

\newpage
\fontsize{8.35pt}{9.4pt}\selectfont

{\LARGE\bfseries\color{ophblue}Scale certificate and gravity}\hfill
{\normalsize \(P\) fixes the cell ratio; \(N\) fixes global capacity}\par
{\scriptsize Paper release: \texttt{\OPHPaperReleaseID}\quad Released: \OPHPaperReleaseDate}\par
\begin{banner}
\centering
{\Large\bfseries the SI scale certificate fixes the area quantum; the pixel cancels.}
\end{banner}

\begin{multicols}{3}
\raggedcolumns

\sect{6. What \(P\) and \(N\) determine}
The two closure coordinates fix dimensionless geometry:
\[
  P_\star=\frac{a_{\rm cell}}{\ell_\star^2},
  \qquad
  N_\star=\frac{A_{\rm dS}}{4\ell_\star^2}
  =
  \frac{3\pi}{\Lambda_\star\ell_\star^2}.
\]
Define \(B_\ell:=\Lambda_\star N_\star\).  Then
\[
  \Lambda_\star\ell_\star^2=\frac{3\pi}{N_\star},
  \qquad
  \Lambda_\star a_{\rm cell}=\frac{3\pi P_\star}{N_\star},
\]
\[
  B_\ell\ell_\star^2=3\pi,
  \qquad
  B_\ell a_{\rm cell}=3\pi P_\star.
\]
These are exact OPH geometry invariants.

\textbf{Scale theorem.}
For any \(\lambda>0\), rescale lengths by
\[
\ell_\star^2\mapsto\lambda^2\ell_\star^2,\quad
a_{\rm cell}\mapsto\lambda^2a_{\rm cell},\quad
\Lambda_\star\mapsto\lambda^{-2}\Lambda_\star.
\]
Then \(P_\star\) and \(N_\star\) are unchanged, while
\[
  B_\ell=\Lambda_\star N_\star
  \mapsto
  \lambda^{-2}B_\ell .
\]
Thus \(P_\star,N_\star\) determine \(B_\ell\ell_\star^2=3\pi\), not
\(B_\ell\) in \({\rm m^{-2}}\).

\textbf{SI scale certificate.}
The selected SI scale branch supplies
\[
  B_\ell=\Lambda_\star N_\star,
\]
where \(\Lambda_\star\) is an observer-facing de Sitter curvature coordinate
read independently of Newton's constant.  The branch certificate is
\[
\begin{gathered}
B_\ell=
3.607873914680321576051841480160172547687708307217\\
1853821242070198789871988886
\times10^{70}{\rm m^{-2}} .
\end{gathered}
\]
Then
\[
\begin{gathered}
\ell_\star^2=\frac{3\pi}{B_\ell}\\
=
2.61228030237427777887347769215451001461202676866\\
\times10^{-70}{\rm m^2}.
\end{gathered}
\]

In reverse-engineering mode, a late-time curvature estimate
\[
  \Lambda_{\rm obs}=\frac{3\Omega_\Lambda H_0^2}{c^2}
  \simeq1.09091050283809\times10^{-52}{\rm m^{-2}}
\]
locates the branch.  The displayed certificate then corresponds to
\[
  N_\star\simeq
  3.3072134747022262700115238431483979537\times10^{122}.
\]

\columnbreak

\sect{7. Meaning of the local quantities}
The local OPH cell has two readings.

\[
  a_{\rm cell}=P_\star\ell_\star^2
  \qquad\hbox{local screen-cell area}
\]
\[
  \bar\ell_{\rm shared}(P_\star)=\frac{P_\star}{4}
  \qquad\hbox{shared edge entropy}
\]

These two readings describe the same elementary observer-cell interface.  The
first is geometric.  The second is entropic.

For a cut of \(N_\Sigma\) cells,
\[
  A(\partial C)=N_\Sigma a_{\rm cell},
  \qquad
  S_{\rm edge}=N_\Sigma\bar\ell_{\rm shared}.
\]
The area law defines the geometric Newton coupling:
\[
  S_{\rm edge}=\frac{A(\partial C)}{4G_{\rm geom}} .
\]

\sect{8. Cancellation}
Substitute the two OPH cell readings into the area law:
\[
  N_\Sigma\bar\ell_{\rm shared}
  =
  \frac{N_\Sigma a_{\rm cell}}{4G_{\rm geom}} .
\]
Cancel the cut size \(N_\Sigma\):
\[
  G_{\rm geom}
  =
  \frac{a_{\rm cell}}{4\bar\ell_{\rm shared}} .
\]
Insert the fixed OPH readings:
\[
\begin{aligned}
  G_{\rm geom}
  &=
  \frac{P_\star\ell_\star^2}{4(P_\star/4)}\\
  &=
  \ell_\star^2 .
\end{aligned}
\]
The local pixel value \(P_\star\) cancels exactly.  Its role is structural: it
makes the cell-area reading and the edge-entropy reading refer to the same
observer-cell unit.

\sect{9. SI conversion}
The OPH geometric readout is an area:
\[
  G_{\rm geom}=\ell_\star^2 .
\]
SI writes the same coupling through
\[
  \ell^2=\frac{\hbar G_{\rm SI}}{c^3}.
\]
Therefore
\[
  G_{\rm SI}=\frac{c^3}{\hbar}\ell_\star^2 .
\]
Use exact SI definitions
\[
  c=299792458~{\rm m\,s^{-1}},
  \qquad
  \hbar=\frac{6.62607015\times10^{-34}}{2\pi}~{\rm J\,s}.
\]

\sect{10. Numerical readout}
\[
\begin{aligned}
G_{\rm OPH}
&=
\frac{(299792458)^3}{6.62607015\times10^{-34}/(2\pi)}
\ell_\star^2 .
\end{aligned}
\]
\[
\begin{gathered}
G_{\rm OPH}
=
6.6742999959105279999999999999999999999999999999986\\
\times10^{-11}
~{\rm m^3\,kg^{-1}\,s^{-2}} .
\end{gathered}
\]

\begin{resultbox}
\centering
{\bfseries\color{ophblue}OPH gravity readout}\par
\vspace{0.10em}
{\fontsize{11.2pt}{12.4pt}\selectfont\bfseries\color{ophblue}
\(G_{\rm OPH}=6.674299995910528\times10^{-11}\)}\par
{\footnotesize \({\rm m^3\,kg^{-1}\,s^{-2}}\)}\par
\vspace{0.08em}
{\scriptsize CODATA reference:
\(6.67430(15)\times10^{-11}~{\rm m^3\,kg^{-1}\,s^{-2}}\).}
\end{resultbox}

\sect{11. Dependency order and downstream rows}
\[
P_\star=\Gamma(P_\star),
\qquad
N_\star=\mathcal C(N_\star),
\qquad
B_\ell=\Lambda_\star N_\star.
\]
\[
B_\ell\ell_\star^2=3\pi,
\qquad
\ell_\star^2=3\pi/B_\ell.
\]
\[
P_\star\to
\bar\ell_{\rm shared}=P_\star/4,
\qquad
(P_\star,\ell_\star^2)\to
a_{\rm cell}=P_\star\ell_\star^2 .
\]
\[
(a_{\rm cell},\bar\ell_{\rm shared})
\to
G_{\rm geom}=\ell_\star^2,
\qquad
(c,\hbar)\to
G_{\rm SI}=c^3\ell_\star^2/\hbar .
\]
Once \(P_\star\), \(N_\star\), and the SI scale certificate are fixed, every
downstream OPH constant is a theorem-grade branch readout, a declared
validation surface, or a continuation target with its status recorded:
\[
  X_i=\mathcal R_i(P_\star,N_\star,\ell_\star^2).
\]
The de Sitter display is one such downstream readout:
\[
  \Lambda_{\rm CRC}=\frac{3\pi}{G_{\rm geom}N_\star}.
\]
The gravity calculation uses the fixed area quantum before this identity is
evaluated.

\begin{greenbox}
\textbf{Conclusion.}
Observation gives the basin.  OPH gives the fixed closure coordinates and the
dimensionless geometry on their declared branches.  The SI scale certificate
supplies the SI value of \(B_\ell=\Lambda_\star N_\star\).  The pixel cancels in the area law.
The readout is
\[
  \boxed{G_{\rm SI}=\frac{c^3}{\hbar}\,\ell_\star^2} .
\]
All other rows keep their theorem, validation, or continuation status.
\textbf{QED.}
\end{greenbox}

\end{multicols}
\end{document}
